We will use the `mtcars dataset` to explore the *ggplot2* package in R 

```{r}
library('ggplot2')
```
Lets breakdown this code:
**aes()** is a function that specifies desired graphing aesthetics. Within this function we are stating what variable our x and y axis will contain. 
**geom_point()** will create a scatterplot.

```{r}
ggplot(mtcars, aes(x=mpg, y=wt))+geom_point()
```

Lets add a title and labels for the x and y axis!

```{r}
ggplot(mtcars, aes(x=mpg, y=wt))+geom_point()+ggtitle('Miles per Gallon vs. Weight')+ labs(x='Miles per Gallon', y='Weight')
```

Next lets center the title!

```{r}
ggplot(mtcars, aes(x=mpg, y=wt))+geom_point()+ggtitle('Miles per Gallon vs. Weight')+ labs(x='Miles per Gallon', y='Weight')+theme(plot.title=element_text(hjust=0.5))
```

Lets add a regression line using the function **geom_smooth()**. We will be using the method *lm* within this function to fit a linear model. 
We will use the default values for this function (a confidence interval of 0.95 will be displayed)

```{r}
ggplot(mtcars, aes(x=mpg, y=wt))+geom_point()+ggtitle('Miles per Gallon vs. Weight')+ labs(x='Miles per Gallon', y='Weight')+theme(plot.title=element_text(hjust=0.5))+geom_smooth(method=lm)
```

Finally we will add a little color to the graph!

```{r}
ggplot(mtcars, aes(x=mpg, y=wt))+geom_point(color = 'navyblue')+ggtitle('Miles per Gallon vs. Weight')+ labs(x='Miles per Gallon', y='Weight')+theme(plot.title=element_text(hjust=0.5))+geom_smooth(method=lm, color='brown4', fill='rosybrown2')
```
